Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
resolving citation.

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to require more details and drive the
implementation closer to the desired goal.  Rinse and repeat.

@@

\noindent Note that the {\tt placeholders} library provides better keywords such as {\tt notImplemented} and {\tt todo} and they tells source locations when executed.
Next we write user documentation in Haddock markup:

@@

\begin{itemize}
\item We use a preprocessor (the {\tt hspec-discover} package\footnote{%
http://hackage.haskell.org/package/hspec-discover}) to automatically generate this boilerplate.
\end{itemize}

>>>>

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.

@@

\noindent Note that the {\tt placeholders} library provide better keyword such as {\tt notImplemented} and {\tt todo}.
Next we write user documentation in Haddock markup:

@@

\begin{itemize}
\item We use a preprocessor (the {\tt hspec-discover} package) to automatically generate this boilerplate.
\end{itemize}
